Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-11-20 paper.tex
Add 85 & 95 real result

\subsection{First Phase}

\subsubsection{Extend Algebraic Connectivity}
Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.

@@

For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
from small to big, output ordered list denoted as $\Gamma$: 
\begin{equation}
	\Gamma = {..., l_i, ..., l_j, ...}
\end{equation}
where $\Delta_{l_i} < \Delta_{l_j}$.

>>>>

\subsection{Extend Algebraic Connectivity}
Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.

@@

For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
from small to big, output ordered list denoted as $\Gamma$: 
\begin{equation}
	\Gamma = \{..., l_i, ..., l_j, ...\}
\end{equation}
where $\Delta_{l_i} < \Delta_{l_j}$.
